Exercise~3.20

### 2022-06-02 airy-resurgence.tex
Start writing about integral equations
Also, add Alex's comments on Andy's exercise

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\let\Re\relax
\DeclareMathOperator{\Re}{Re}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\series}[1]{\tilde{#1}}
\newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
\DeclareMathOperator{\Ai}{Ai}

@@

The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$. Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest. Let $F = \laplace_{\zeta, 0} f$. Equation~1.8 of \ref{laplace-tfm} shows\footnote{The argument cited still works in our generality. For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
\subsubsection{Action on integral operators}\label{L-int-op}
When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
\end{equation}
for all integers $n \ge 0$. You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
for all $\lambda \in (0, \infty)$.

\color{violet}
When $\varphi$ is $n$ times differentiable, its $n$th derivative is in $\mathcal{E}$, and its zeroth through $(n - 1)$st derivatives extend continuously to zero, integration by parts gives the formula
\begin{align}\label{id:L-diff}
\laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \varphi & = z^n \laplace_\zeta \varphi - \left[ \varphi\,z^{n-1} + \varphi'\,z^{n-2} + \varphi''\,z^{n-3} + \ldots + \varphi^{(n-1)} \right]_{\zeta = 0} \\
& = z^n\,\laplace\left( \varphi - \left[ \varphi + \varphi'\,\zeta + \tfrac{\varphi''}{2!}\,\zeta^2 + \ldots + \tfrac{\varphi^{(n-1)}}{(n-1)!}\,\zeta^{n-1} \right]_{\zeta = 0} \right). \nonumber
\end{align}
Note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O_{\zeta \to \infty}(e^{c\zeta})$. Then \[ \left|\int_0^Z f'\,d\zeta\right| \le \int_0^Z |f'|\,d\zeta \lesssim \int_0^Z e^{c\zeta}\,d\zeta = \tfrac{1}{c}(e^{cZ} - 1) \lesssim e^{cZ}.\] Now we know the integral on the left-hand side converges, implying that $f$ extends continuously to zero, with $|f - f_{\zeta = 0}| \lesssim e^{c\zeta}$.}
\subsection{Algebraic version}
\subsubsection{Definition}
Let $\mathcal{P}_\zeta$ be the vector space spanned by $\zeta^\alpha$ for $\alpha \in \R \smallsetminus \Z_{< 0}$. Note that $\mathcal{P}_\zeta \cap \mathcal{E}_\zeta$ is $\mathcal{P}_\zeta^{> -1}$, the subspace spanned by $\zeta^\alpha$ with $\alpha > -1$. Since
\[ \laplace_\zeta(\zeta^\alpha) = \Gamma(\alpha+1)\,z^{-(\alpha + 1)} \]
for all $\alpha > -1$, let's use the same formula to extend $\laplace_\zeta$ to all of $\mathcal{P}_\zeta$. This defines $\laplace_\zeta$ consistently on $\mathcal{E}_\zeta + \mathcal{P}_\zeta$.
\subsubsection{Action on differential operators}\label{L-diff-op-alg}
Observe that
\[ \laplace_\zeta(\zeta^{\alpha + 1}) = -\tfrac{\partial}{\partial z}\,\laplace_\zeta(\zeta^\alpha) \]
for $\alpha \neq -1$. This extends identity~\ref{id:L-mult} to all of $\mathcal{P}_\zeta$.

Observe that
\[ \laplace_\zeta\tfrac{\partial}{\partial \zeta}(\zeta^\alpha) = \begin{cases}
z\,\laplace_\zeta(\zeta^\alpha) & \alpha \neq 0 \\
0 & \alpha = 0,
\end{cases} \]
and that $0 = z\,\laplace_\zeta(1) - 1$. This recovers identity~\ref{id:L-diff} for any function in $\mathcal{P}_\zeta$ whose $n$th derivative is in $\mathcal{P}_\zeta^{> -1}$. Although the functions in $\mathcal{P}_\zeta^{< 0}$ are singular at zero, let's pretend they vanish at zero. With that convention, formula~\ref{id:L-diff} extends to all of $\mathcal{P}_\zeta$.

Now we have the results of Section~\ref{L-diff-op} for all functions in $\mathcal{E}_\zeta + \mathcal{P}_\zeta$. Identity~\ref{id:L-diff} is particularly simple when $\varphi$ has a {\em fractional power singularity} \textcolor{magenta}{[new terminology: when $\varphi$ is {\em slight}]} at $\zeta = 0$. By this, I mean that $\varphi$ can be written as $\varphi_\text{frac} + \varphi_\text{reg}$, where $\varphi_\text{frac} \in \mathcal{P}_\zeta$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\varphi_\text{reg} \in \mathcal{E}_\zeta$ vanish at zero. Under this condition, all the initial value terms in the identity vanish, leaving
\[ \laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \varphi = z^n \laplace_\zeta \varphi. \]
\color{black}
\subsection{Change of translation chart}\label{translation}
Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
\begin{align*}
\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
\end{align*}
we learn that
\[ \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi. \]
\subsection{Rescaling of translation structure}
Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$. The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure. The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$. From the calculation
\begin{align*}
\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
& = \mu\,\laplace_{\zeta, 0} \varphi
\end{align*}
we learn that
\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure. We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
\section{Shifting integro-differential equations}\label{shifting}
Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$. A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point. We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
\begin{equation}\label{eqn:slight-defn}
\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
\end{equation}
where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.

>>>>

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\let\Re\relax
\DeclareMathOperator{\Re}{Re}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\series}[1]{\tilde{#1}}
\newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
\newcommand{\holoL}[1]{\mathcal{H}L^{#1}}
\DeclareMathOperator{\Ai}{Ai}

@@

The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$. Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest. Let $F = \laplace_{\zeta, 0} f$. Equation~1.8 of \ref{laplace-tfm} shows\footnote{The argument cited still works in our generality. For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
\subsubsection{Action on integral operators}\label{L-int-op}
When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
\end{equation}
for all integers $n \ge 0$. You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
for all $\lambda \in (0, \infty)$.
\subsection{Change of translation chart}\label{translation}
Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
\begin{align*}
\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
\end{align*}
we learn that
\[ \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi. \]
\subsection{Rescaling of translation structure}
Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$. The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure. The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$. From the calculation
\begin{align*}
\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
& = \mu\,\laplace_{\zeta, 0} \varphi
\end{align*}
we learn that
\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure. We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
\section{Integro-differential equations}
\subsection{Existence of solutions}
\subsubsection{Function spaces for contour integration}
Take a simply connected open set $\Omega$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. Let $\mathcal{S} \subset \holoL{\infty}(\Omega)$ be the union of $O_{\zeta, 0 \leftarrow}(\zeta^\tau)$ over all $\tau > 0$.

If you give a Riemann surface a metric which is compatible with its conformal structure, you get a norm on each tangent space. A {\em density} on a Riemann surface is a norm that arises in this way. Given a density $\rho$ on $\Omega$, let $\ell_\rho$ be the continuous function on $\Omega$ that measures distance from $\zeta = 0$ with respect to $\rho$. The value of $\ell_\rho$ at $a \in \Omega$ is the infimal length of a rectifiable path that runs from $\zeta = 0$ to $a$ within $\Omega$. Keep in mind that $\Omega$ touches but doesn't contain $\zeta = 0$, and $\ell_\rho$ is only well-defined when $\rho$ puts $\zeta = 0$ at finite distance from the points in $\Omega$. \textcolor{magenta}{[...]}

\color{gray}
A bounded holomorphic map
\begin{align*}
\Omega & \to \holoL{1}(\Omega) \\
\alpha & \mapsto g_\alpha
\end{align*}
defines a bounded linear operator
\[ \mathcal{G}f\big|_{\zeta = \alpha} = \int_0^\alpha  g_\alpha f \]
on $\holoL{\infty}(\Omega)$. Noting that
\color{black}

%%with\footnote{We're using the operator norm on the left-hand side and the $L^1$ norm on the right-hand side.} $\|\mathcal{G}\| = \sup_{\alpha \in \Omega} \|g_\alpha\|_1$.
\subsection{Order shifting}\label{shifting}
Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$. A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point. We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
\begin{equation}\label{eqn:slight-defn}
\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
\end{equation}
where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.

### 2022-06-02 exercise-3.20.tex
Start writing about integral equations
Also, add Alex's comments on Andy's exercise

\begin{document}
\maketitle
Let $\mathcal{D}$ be the noncommutative $\C$-algebra generated by the number operator $N$ and the lowering operator $A$, with the relation $NA = A(N-1)$. Let $N$ act as $t \tfrac{\partial}{\partial t}$ on $\C\llparenthesis t \rrparenthesis$ and $\zeta \tfrac{\partial}{\partial \zeta}$ on $\C\llparenthesis \zeta \rrparenthesis$. Let $A$ act as $t^{-1}$ on $\C\llparenthesis t \rrparenthesis$ and
\begin{align*}
\frac{\zeta^n}{n!} & \mapsto \frac{\zeta^{n-1}}{(n-1)!} & n & > 0 \\
\zeta^n & \mapsto \zeta^{n-1} & n & \le 0
\end{align*}
on $\C\llparenthesis \zeta \rrparenthesis$. These actions commute with the physicist's Borel transform
\begin{align*}
\phborel \maps \C\llbracket t \rrbracket & \to \C\llbracket \zeta \rrbracket \\
t^n & \mapsto \frac{\zeta^n}{n!}
\end{align*}
whenever both paths through the commutative square are well-defined.
\begin{exr}
Suppose $f \in \C\llbracket t \rrbracket$ is annihilated by $D \in \mathcal{D}$. Prove that $\phborel f \in \C\llbracket \zeta \rrbracket$ is annihilated by the operator $\dict(D)$ given by the alternate representation
\begin{align*}
\dict \maps \mathcal{D} & \to \big\{\C\llbracket \zeta \rrbracket \to \C\llparenthesis \zeta \rrparenthesis\big\} \\
A & \mapsto \tfrac{\partial}{\partial \zeta} \\
N & \mapsto \zeta \tfrac{\partial}{\partial \zeta}.
\end{align*}
\end{exr}
\begin{proof}[Solution]
Moving $A$ to the right, we can write
\begin{align*}
D & = P_0(N)\,A^n + P_1(N)\,A^{n-1} + \ldots + P_{n-1}(N)\,A + P_n(N) \\
\dict(D) & = P_0(N)\,\big(\tfrac{\partial}{\partial \zeta}\big)^n + P_1(N)\,\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} + \ldots + P_{n-1}(N)\,\tfrac{\partial}{\partial \zeta} + P_n(N)
\end{align*}
in terms of polynomials $P_0, \ldots, P_n$. Notice that $\big(\tfrac{\partial}{\partial \zeta}\big)^k = \Pi A^k$, where $\Pi$ is the projection $\C\llparenthesis \zeta \rrparenthesis \to \C\llbracket \zeta \rrbracket$ in the monomial basis. Since $\Pi$ commutes with $N$, it follows that $\dict(D) = \Pi D$. Since the action of $\mathcal{D}$ commutes with $\phborel$, the assumption that $Df = 0$ implies that
\begin{align*}
\dict(D)\,\phborel f & = \Pi D \phborel f \\
& = \Pi \phborel Df \\
& = 0.
\end{align*}
\end{proof}
\end{document}

>>>>

\begin{document}
\maketitle
Let $\mathcal{D}$ be the noncommutative $\C$-algebra generated by the number operator $N$ and the lowering operator $A$, with the relation $NA = A(N-1)$. Let $N$ act as $t \tfrac{\partial}{\partial t}$ on $\C\llparenthesis t \rrparenthesis$ and $\zeta \tfrac{\partial}{\partial \zeta}$ on $\C\llparenthesis \zeta \rrparenthesis$. Let $A$ act as $t^{-1}$ on $\C\llparenthesis t \rrparenthesis$ and
\begin{align*}
\frac{\zeta^n}{n!} & \mapsto \frac{\zeta^{n-1}}{(n-1)!} & n & > 0 \\
\zeta^n & \mapsto \zeta^{n-1} & n & \le 0
\end{align*}
on $\C\llparenthesis \zeta \rrparenthesis$. These actions commute with the physicist's Borel transform
\begin{align*}
\phborel \maps \C\llbracket t \rrbracket & \to \C\llbracket \zeta \rrbracket \\
t^n & \mapsto \frac{\zeta^n}{n!}
\end{align*}
whenever both paths through the commutative square are well-defined.
\begin{exr}
Suppose $f \in \C\llbracket t \rrbracket$ is annihilated by $D \in \mathcal{D}$. Prove that $\phborel f \in \C\llbracket \zeta \rrbracket$ is annihilated by the operator $\dict(D)$ given by the alternate representation
\begin{align*}
\dict \maps \mathcal{D} & \to \big\{\C\llbracket \zeta \rrbracket \to \C\llparenthesis \zeta \rrparenthesis\big\} \\
A & \mapsto \tfrac{\partial}{\partial \zeta} \\
N & \mapsto \zeta \tfrac{\partial}{\partial \zeta}.
\end{align*}
\end{exr}
\begin{proof}[Solution]
Moving $A$ to the right, we can write
\begin{align*}
D & = P_0(N)\,A^n + P_1(N)\,A^{n-1} + \ldots + P_{n-1}(N)\,A + P_n(N) \\
\dict(D) & = P_0(N)\,\big(\tfrac{\partial}{\partial \zeta}\big)^n + P_1(N)\,\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} + \ldots + P_{n-1}(N)\,\tfrac{\partial}{\partial \zeta} + P_n(N)
\end{align*}
in terms of polynomials $P_0, \ldots, P_n$. Let $\Pi$ be the projection $\C\llparenthesis \zeta \rrparenthesis \to \C\llbracket \zeta \rrbracket$ in the monomial basis. Notice that $\big(\tfrac{\partial}{\partial \zeta}\big)^k$ and $\Pi A^k$ act the same on elements of $\C\llbracket \zeta \rrbracket$. Since $\Pi$ commutes with $N$, it follows that $\dict(D) = \Pi D$. Since the action of $\mathcal{D}$ commutes with $\phborel$, the assumption that $Df = 0$ implies that
\begin{align*}
\dict(D)\,\phborel f & = \Pi D \phborel f \\
& = \Pi \phborel Df \\
& = 0.
\end{align*}
\end{proof}
{\it Note from Alex: For holomorphic functions, the correct statement might be that $Df = 0$ implies $\tfrac{\partial}{\partial \zeta} \mathcal{F}(D)\,\phborel f = 0$. The idea is that $\mathcal{F}(A)$ only differs from $A$ because it annihilates constants, so a ``translation error'' in the differential equation can only leave constants left over.}
\end{document}
